working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances). Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits. In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.

@@

>>>>

In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (Vegan package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits. Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments. To find a model with the best explanatory traits we used the function **bioenv** from R. We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits. Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits. In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.

@@

Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a statistically clear correlation for both markers (p<0.05). The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test between the assymetrical matrix
of heterospecific pollen effect (10 by 10 matrix) with the different
distance matrices of traits (Euclidean distances). Heterospecific pollen
effect was obtained through the subtraction of seed production by hand
cross-pollination minus seed production of the different heterospecific
pollen treatments. To find a model with the best explanatory traits we
used the function \textbf{bioenv} from R. We also conducted Mantel test
between the matrix of heterospecific pollen effect and the distance
matrix from all the traits. Moreover, we explored also the correlation
between traits and heterospecific pollen effect through generalized
mixed models where the response variable was heterospecific pollen
effect and the explanatory variable the different traits. In addition,
we tested the correlation between the total amount of pollen deposited
on the stigma with heterospecific pollinations and the stigma size
through Pearson's correlation.

@@

>>>>

In order to test the relative effect of traits on seed production with
foreign pollen we performed Mantel test in R (Vegan package, Euclidean
distance) between the assymetrical matrix of heterospecific pollen
effect (10 by 10 matrix) with the different distance matrices of traits.
Heterospecific pollen effect was obtained through the subtraction of
seed production by hand cross-pollination minus seed production of the
different heterospecific pollen treatments. To find a model with the
best explanatory traits we used the function \textbf{bioenv} from R. We
also conducted Mantel test between the matrix of heterospecific pollen
effect and the distance matrix from all the traits. Moreover, we
explored also the correlation between traits and heterospecific pollen
effect through generalized mixed models where the response variable was
heterospecific pollen effect and the explanatory variable the different
traits. In addition, we tested the correlation between the total amount
of pollen deposited on the stigma with heterospecific pollinations and
the stigma size through Pearson's correlation.

@@

Results of Mantel test between heterospecific pollen effect and
phylogenetic distance gave a statistically clear correlation for both
markers (p\textless{}0.05). The correlations with ITS and RBCL markers
was respectively of 0.29 and 0.25.
